Spatial Relational Models for Neural Circuit Discovery

### 2013-10-20 docs/techreport.tex
updates to figures

\subsection{Inference}
\subsubsection{Structural Inference}

@@

>>>>

\subsection{Inference}

We use Markov-chain Monte Carlo techniques to sample from the posterior 
distribution of our model conditioned on the data. Inference is
performed over cluster assignments, the per-component latent parameters, 
and the per-relation, datatype-specific parameters.

\subsubsection{Structural Inference}
Algorithm 8 from radford neal \cite{nealalgo8}

@@

\subsubsection{Annealing}
For many examples of the data here we perform annealing.
